---
title: "Chinese Economy Snapshot"
date: "July 2021"
output: ioslides_presentation
---

<!-- TODO: Blank page after Title page -->

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(patchwork)
library(scales)
```

```{r, include=FALSE}
ggplot2::theme_set(theme_bw() + theme(
  panel.grid.major.x = element_blank(), 
  panel.grid.minor.x = element_blank(), 
  panel.grid.minor.y = element_blank(),
  strip.background = element_blank(),
  legend.title = element_blank(), 
  legend.position = "bottom", 
  axis.title = element_blank(),
  plot.caption = element_text(hjust=0),
  plot.title = element_text(hjust=.5)
  ))
# ggplot2::update_geom_defaults("line", list(color="red"))
```

```{r, include=FALSE}
source("ceic.R")
ceic <- ceic_load("data.m")
data <- ceic$fetch_all()
#saveRDS(data, "data.Rda")
```

```{r, include=FALSE}
# data <- readRDS("data.Rda")
# meta <- names(data) %>% as_tibble()
# meta %>% write_csv("meta.csv")
```

```{r, include=FALSE}
shorten_name <- function(name, level=1, prefix=NULL, suffix=NULL, exclude=NULL) {
  map_chr(name, function(.name) {
    trms <- str_split(.name, ": ", simplify = T)
    excl <- str_c(c("CN", "YoY", "ytd", exclude), collapse = "|")
    subs <- str_subset(trms, excl, negate = T)
    comb <- str_c(tail(subs, level), collapse = ":")
    str_c(prefix, comb, suffix, sep = " ")
  })
}
```

```{r time-horizon, include=FALSE}
last_one_year <- 12
last_two_years <- 12*2
last_three_years <- 12*3
last_five_years <- 12*5
last_ten_years <- 12*10
last_forty_years <- 12*20
```

<!-- # Overview -->

## Gross Demestic Product

```{r}
data %>% 
  select(date, GDP = `CN: GDP`, `GDP Gap` = `CN: GDP: ytd`) %>% 
  tail(last_ten_years) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(value = value*10^9) %>% 
  ggplot(aes(date, value, col=name)) + 
  geom_line() + 
  scale_y_continuous(labels = label_number_si()) + 
  facet_wrap(~name, scales = "free_y") +
  theme(legend.position = "none", aspect.ratio = .8) + 
  labs(caption = "Seasonally adjusted quarterly data")
```

## Inflation

```{r}
data %>% select(date, 
         CPI = `CN: Consumer Price Index`, 
         `Core CPI` = `CN: CPI: Core (excl. Food & Energy)`,
         PPI = `CN: Producer Price Index(PPI)`) %>% 
  tail(last_ten_years) %>% 
  pivot_longer(!date) %>% 
  mutate(group=if_else(name=="PPI", "Producer Price", "Consumer Price")) %>% 
  ggplot(aes(date, value, col=name)) + 
  facet_wrap(~group) + geom_line() +
  theme(aspect.ratio = 0.8) +
  labs(caption = "Last year = 100")
```

## Unemployment

```{r}
data %>% 
  select(date, contains(c("Unemployment", "Employment: Urban: New Increased"))) %>% 
  tail(last_five_years) %>% 
  fill(!date, .direction = "up") %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name, 2)) %>% 
  mutate(group=if_else(str_detect(name, "Unemployment"), "Unemployment Rate", "New Urban Employment")) %>% 
  mutate(value=if_else(group=="New Urban Employment", value*1000, value)) %>% 
  ggplot(aes(date, value, col=label)) + geom_line() +
  facet_wrap(~group, scales = "free_y") +
  scale_y_continuous(labels = label_number_si()) +
  theme(aspect.ratio = .8)
```

## National Debt / GDP

```{r}
data %>% 
  select(date, contains("Leverage Ratio")) %>% 
  tail(last_forty_years) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(x=date, y=value, color=label)) + 
  geom_line()
```

<!-- # Economic Activity -->

## PMI: Manufacturing

```{r}
data %>% 
  select(date, contains("PMI: Mfg")) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name, level = 2)) %>% 
  ggplot(aes(x=date, y=label, fill=value)) + geom_tile() + 
  scale_x_date(date_breaks = "3 months", labels = label_date_short(), expand = c(0,0)) +
  scale_fill_gradient2(low = "steelblue4", high = "red4", midpoint = 50) +
  scale_y_discrete(position = "right", expand = c(0,0))
```

## PMI: Non-manufacturing

```{r}
P1 <- data %>% 
  select(date, contains("PMI: Service")) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name, level = 2)) %>% 
  ggplot(aes(x=date, y=label, fill=value)) + geom_tile() + 
  scale_x_date(date_breaks = "3 months", labels = label_date_short(), expand = c(0,0)) +
  scale_fill_gradient2(low = "steelblue4", high = "red4", midpoint = 50) +
  scale_y_discrete(position = "right", expand = c(0,0)) +
  theme(legend.position = "none")

P2 <- data %>% 
  select(date, contains("PMI: Construction")) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name, level = 2)) %>% 
  ggplot(aes(x=date, y=label, fill=value)) + geom_tile() + 
  scale_x_date(date_breaks = "3 months", labels = label_date_short(), expand = c(0,0)) +
  scale_fill_gradient2(low = "steelblue4", high = "red4", midpoint = 50) +
  scale_y_discrete(position = "right", expand = c(0,0))

P1 / P2
```

## Electricity and Transportation

```{r}
data %>% 
  select(date, contains(c("Freight Traffic", "Electricity Production"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  facet_wrap(~label, scales = "free_y") +
  theme(legend.position = "none", aspect.ratio = .8) +
  labs(caption = "Sum of trailing 12 months")
```

## Retail Sales

```{r}
data %>% 
  select(date, `Retail Sales` = `CN: Retail Sales of Consumer Goods`, 
         `Online Retail Sales (YoY)` = `CN: Online Retail Sales: ytd: Goods and Service`) %>% 
  tail(last_five_years) %>% 
  fill(`Online Retail Sales (YoY)`, .direction = "up") %>% 
  mutate(`Retail Sales` = `Retail Sales` * 10^9) %>% 
  pivot_longer(!date) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  facet_wrap(~name, scales = "free_y") +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "none", aspect.ratio = .8) + 
  labs(caption = "Sales volume seasonally adjusted")
```

<!-- ## Online Sales and Volume -->

## Industrial Production

```{r}
data %>% 
  select(date, contains("Industrial Production")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(x=date,y=value, col=name)) + geom_line() + 
  scale_y_continuous(labels = label_number_si()) +
  facet_wrap(.~label, scales = "free_y") +
  theme(legend.position = "none")
```

<!-- # Money and Financing -->

## Money Supply

```{r}
data %>% 
  select(date, contains("Money Supply")) %>% 
  mutate_at(vars(ends_with(c("M1", "M2"))), ~.*10^9) %>% 
  tail(last_three_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label = substring(name, 4)) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() + 
  scale_y_continuous(labels = label_number_si()) +
  facet_wrap(~label, scales = "free_y") +
  theme(legend.position = "none")
```

## Aggregate Financing

```{r}
data %>% 
  select(date, contains("Aggregate Financing")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label = shorten_name(name)) %>% 
  mutate(value = value*10^9) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  facet_wrap(~label, scales = "free_y") +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "none") +
  labs(caption = "Sum of trailing 12 months")
```

## Bank Loans

```{r}
data %>% 
  select(date, contains("Loan: New Increased")) %>% 
  tail(last_ten_years) %>% 
  pivot_longer(!date) %>% 
  mutate(group=if_else(str_detect(name, "Household"), "Households", "Corporates")) %>% 
  mutate(label=shorten_name(name)) %>% 
  mutate(value=value * 10^9) %>% 
  ggplot(aes(date, value, col=label)) + geom_line() +
  facet_wrap(~group, scales = "free_y") +
  scale_y_continuous(labels = label_number_si()) +
  labs(caption = "Sum of trailing 12 months") +
  theme(aspect.ratio = .8)
```

<!-- ## Loan Prime Rate (LPR) -->

```{r, include=FALSE}
data %>% 
  select(date, contains("Loan Prime Rate")) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!date) %>% 
  ggplot(aes(date, value, col=name)) +
  geom_line()
```

## Interest Rates

```{r}
data %>% 
  select(date, contains(c("SHIBOR", "R007", "Treasury Bond Yield"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(group = if_else(name %>% str_detect("Treasury"), "Treasury Yield", "Interbank Rate")) %>% 
  mutate(label = shorten_name(name, level=1)) %>% 
  ggplot(aes(date, value, col=label)) + 
  facet_wrap(~group) + geom_line() +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) +
  theme(aspect.ratio = .8)
```

<!-- # Business -->

## Industrial Enterprises

```{r}
data %>% 
  select(date, contains(c("Industrial Enterprise", "Industrial Capacity"))) %>% 
  mutate_at(vars(contains(c("Revenue", "Profit"))), ~.*10^9) %>% 
  mutate_at(vars(contains("Inventory")), ~.*100) %>% 
  tail(last_five_years) %>% 
  fill(!date, .direction = "up") %>% 
  pivot_longer(!date) %>% 
  mutate(label = shorten_name(name, level=2)) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  scale_y_continuous(labels = label_number_si()) +
  facet_wrap(~label, scales = "free_y") +
  theme(legend.position = "none") +
  labs(caption = "Revenue and profit are sums of trailing 12 months.\nInventory is the seasonally adjusted level as a percentage of trailing 12-month revenue.")
```


<!-- ## Industrial value-added -->

```{r, include=FALSE}
data %>% 
  select(date, contains("Value Added of Industry")) %>% 
  fill(!date, .direction = "down") %>% 
  pivot_longer(!date) %>% 
  ggplot(aes(date, value, color=name)) + geom_line()
```


## Investments

```{r, warning=F}
data %>% 
  select(date, contains(c("Fixed Asset Investment", "Approved Project", "FAI", "FDI"))) %>% 
  mutate_at(vars(contains("Approved Project")), ~.*10^9) %>% 
  mutate_at(vars(contains(c("Fixed Asset Investment: ytd", "FAI", "FDI"))), ~.*10^6) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label = shorten_name(name, level=2)) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  scale_y_continuous(labels = label_number_si()) +
  facet_wrap(~label, scales = "free_y") +
  theme(legend.position = "none") +
  labs(caption = "Sum of trailing 12 months")
```

<!-- # Housing  -->

## Real Estate Sales and Investmant

```{r}
data %>% 
  select(date, contains(c("Real Estate Inv", "Building Sold"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(value = value * 10^6) %>% 
  mutate(label = shorten_name(name, level=1)) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  scale_y_continuous(labels = label_number_si()) +
  facet_wrap(~label, scales = "free_y") +
  labs(caption = "Sum of trailing 12 months") +
  theme(aspect.ratio = .8, legend.position = "none") 
```

## Real Estate: Floor Space

```{r, warning=F}
data %>% 
  select(date, contains("Floor Space")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(value=value*1000) %>% 
  mutate(label=shorten_name(name, exclude="Commodity Bldg")) %>% 
  ggplot(aes(date,value, col=name)) + geom_line() +
  scale_y_continuous(labels = label_number_si()) +
  facet_wrap(~label, scales = "free_y") + 
  theme(legend.position = "none") +
  labs(caption = "Sum of trailing 12 months")
```

## Government Revenue and Expenditure

```{r}
data %>% 
  select(date, contains(c("Govt Revenue", "Govt Expenditure", "Government Revenue"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(group = if_else(name %>% str_detect("Tax|Fund"), 
                         "Sources of Revenue", 
                         "Revenue and Expenditure")) %>%
  mutate(label=shorten_name(name, level=1)) %>% 
  mutate(value = value * 10^9) %>% 
  ggplot(aes(date, value, color=label)) + geom_line() +
  facet_wrap(~group, scales = "free_y") + 
  scale_y_continuous(labels = label_number_si()) +
  theme(aspect.ratio = .8) +
  labs(caption = "Sum of trailing 12 months")
```

## Government Debt Issuance

```{r}
data %>% 
  select(date, contains("Local Government Debt Issuance:")) %>% 
  tail(last_three_years) %>% 
  pivot_longer(!date) %>% 
  mutate(value = value * 10^6) %>% 
  mutate(label = shorten_name(name, 2)) %>% 
  ggplot(aes(date, value, col=name)) + geom_line() +
  facet_wrap(~label) +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "none") +
  labs(caption = "Sum of trailing 12 months")
```

## Trade Balance

```{r}
data %>% 
  select(date, contains(c("Import CIF", "Export FOB", "Trade balance"))) %>% 
  tail(last_ten_years) %>% 
  mutate_at(vars(!date), ~.*10^6) %>% 
  ggplot(aes(x=date)) + 
  geom_line(aes(y=`CN: Export FOB`, col="Export FOB")) + 
  geom_line(aes(y=`CN: Import CIF`, col="Import CIF")) +
  geom_col(aes(y=`CN: Trade Balance`), fill="grey") +
  scale_y_continuous(labels = label_number_si()) +
  labs(caption = "Seasonally adjusted USD")
```

## Balance of Payments

```{r}
data %>% 
  select(date, contains("BoP")) %>% 
  tail(last_ten_years) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(value=value*10^6) %>% 
  mutate(label=shorten_name(name, 2, exclude="BoP")) %>% 
  ggplot(aes(date, value, fill=label)) + 
  geom_col(position = position_stack()) +
  scale_y_continuous(label = label_number_si())
```

## RMB Assets Hold by Foreign Entities

```{r}
data %>% 
  select(date, contains("RMB Financial Asset Held by Overseas Entity")) %>% 
  tail(last_ten_years) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(value = value*10^9) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(date,value,col=name)) + 
  scale_y_continuous(labels = label_number_si()) +
  geom_line() +
  facet_wrap(~label) +
  theme(legend.position = "none")
```

## Equity Market

```{r}
data %>% 
  select(date, contains("CSI 300 Index")) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(date, value,col=label)) + geom_line() +
  facet_wrap(~label, scales = "free_y") +
  scale_x_date(labels = label_date("%m/%y")) +
  theme(legend.position = "none")
```

## Commodity Market

```{r}
data %>% 
  select(date, contains(c("Settlement Price", "CCI"))) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!date) %>% 
  mutate(label=shorten_name(name, exclude="1st Month")) %>% 
  ggplot(aes(date, value, col=label)) + geom_line() +
  scale_x_date(labels = label_date("%m/%y")) +
  facet_wrap(~label, scales = "free_y") + 
  theme(legend.position = "none")
```

## Bond Market 

```{r}
P1<-data %>% 
  select(date, contains("Bond Issuance: PBC:")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(value=value * 10^6) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(date,value,fill=label)) + 
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  labs(caption = "Sum of trailing 12 months") +
  theme(aspect.ratio = .8, legend.position = "none") +
  ggtitle("Bond issuance")

P2<-data %>% 
  select(date, contains("Bond Outstanding: PBC:")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!date) %>% 
  mutate(value=value * 10^6) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(date,value,fill=label)) + 
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  ggtitle("Bond outstanding")

P1 + P2
```

## Labor Employment

```{r}
P1<-data %>% 
  select(date, `CN: Employment: Rural`, `CN: Employment: Urban`) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(value = value*10^6) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(date, value, fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  theme(aspect.ratio = .8)

P2<-data %>% 
  select(date, 
         `CN: Employment: Primary Industry`, 
         `CN: Employment: Secondary Industry`, 
         `CN: Employment: Tertiary Industry`) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(value = value*10^6) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(date, value, fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si())

P1 + P2
```

## Employment: Urban Non-Private

```{r}
data %>% 
  select(date, contains("Employee: Urban Non-private:")) %>% 
  drop_na() %>% 
  pivot_longer(!date) %>% 
  mutate(value = value * 10^6) %>% 
  mutate(label = shorten_name(name) %>% str_trunc(28)) %>% 
  ggplot(aes(date,value,fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "right")
```

## Employment: Private & Individual

```{r}
data %>% 
  select(date, contains("Employee: Private & Individual:")) %>% 
  filter(!is.na(`CN: No of Employee: Private & Individual: Wholesale & Retail Trade`)) %>% 
  pivot_longer(!date) %>% 
  mutate(value = value * 10^6) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(date,value,fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "right")
```

<!-- THE END -->