---
title: "Chinese Economy Chart Pack"
date: "December 2022"
output:
  beamer_presentation: default
  ioslides_presentation: default
---

<!-- General Principles: -->
<!-- * Faithful to official data; use interpolation as less as possible -->
<!-- * Timely changes are most valuable; avoid using YTD or TTM, as they  -->
<!--   dilute most recent changes -->
<!-- * Time series are transformed to present in the most sensible way -->
<!-- * Everything must be seasonally adjusted; X11 method is preferred -->
<!-- * Titles need to be concise and informational; avoid abbreviations -->
<!-- * Column names should be readable, avoid modify column names in code -->
<!-- * Base plot style is preferred, even with ggplot -->
<!-- * Avoid cutting short of time horizon, unless data is unavailable in -->
<!--   early dates or the chart is overloaded with information -->

```{r, include=F}
library(ggplot2)
library(csutil)
library(zoo)
```

```{r data-loading, include=F}
df = parse2DF("data.m")
dfn = read.csv("names.csv")
df = merge(df, dfn, by = c("srCode", "seriesName"))
dfq = subset(df, frequency == "Quarterly")
dfm = subset(df, frequency == "Monthly")
DTQ = grabTS(dfq, out = "zoo") |> window(start=2012)
DTM = grabTS(dfm, out = "zoo") |> window(start=2012)
colnames(DTQ) = dfq$shortName
colnames(DTM) = dfm$shortName
```

```{r global-settings, include=F}
ggplot2::theme_set(
  ggthemes::theme_few() + 
  theme(legend.position = "none", 
        legend.title = element_blank(),
        axis.title.x = element_blank()))
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

## DISCLAIMER {.center}

This chart pack presents a set of key indicators to track China's economic 
conditions and is intended to supplement the official reports from the NBS. 
The time series in this chart pack have been seasonally adjusted and missing 
values interpolated by ourselves, therefore may or may not match the official 
numbers and should be used with caution. The author does not express any 
opinions through this presentation and the user assumes all responsibility 
for relying on the information provided.


## Gross Demestic Product

```{r}
dualplot(
  y1 = DTQ$GDP |> trans(seas="x11", hp_filter="cycle"), 
  y2 = (DTQ$`GDP: QoQ` - 100) * 4, 
         lylim = c(-1000, 1000), rylim = c(-20,20),
         ylab = "GDP Gap (HP-Filtered)", ylab.at = 0,
         rylab = "Quarterly Growth %")
abline(h=0, col="gray")
```

## Inflation

```{r}
dualplot(y1 = DTM$CPI -100, y2 = DTM$PPI - 100, 
         ylab = "CPI (YoY)", rylab = "PPI (YoY)")
```

## Unemployment

```{r}
# surveyed unemployment rates are available from 2013
with(window(DTM, start=2014), {
  dualplot(
    y1 = `New Urban Employment: ytd` |> trans(unit=1/1000, YTD="avg", seas="x11"), 
    y2 = `Unemployment: 31 Cities` |> na.approx(), 
    ylab  = "New Urban Employment (Million)", 
    rylab = "Unemployment Rate (31 Cities)")  
})
```

## Consumption: Retail Sales

```{r, warning=FALSE}
# the level data has very low quality with lots of missing values
# use the seasonally-adjusted mom growth rates to construct an index
dualplot(
  y1 = as.ts(DTM$`RetailSales: mom`/100) |> diffinv(xi=1), 
  y2 = as.ts(DTM$`RetailSales: mom`*12),
  rylim = c(-30,30),
  ylab = "Retail Sales Index", 
  rylab = "MoM Growth (annualized %)")
```


## Fixed Asset Investment

```{r}
# the level data has very low quality with lots of missing values
# use the seasonally-adjusted mom growth rates to construct an index
dualplot(
  y1 = as.ts(DTM$`FAI: mom`/100) |> diffinv(xi=1),
  y2 = as.ts(DTM$`FAI: mom`*12), 
  rylim = c(-30,30),
  ylab = "FAI Index", 
  rylab = "MoM Growth (annualized %)")
```

## Foreign Direct Investment

```{r}
# No missing values in Jan-Feb
# FDI is less prone to LNY holiday; standard x11 applies
dualplot(
  y1 = DTM$`FDI: ytd` |> trans(unit=1/1000, YTD = "d", seas = "x11"), 
  y2 = DTM$`FDI: ytd` |> trans(YTD = "d", chg="yoy"), 
  ylab = "FDI (USD Bn)", rylab = "YoY Growth (%)") 
```

## National Debt / GDP

```{r}
subset(DTQ, select=startsWith(colnames(DTQ), "Leverage")) |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |> 
  ggplot(aes(x = index)) +
  geom_line(aes(y = value, col = name)) +
  facet_wrap(~ name, scales = "free_y") +
  scale_color_manual(values = 2:5) +
  scale_x_continuous(breaks = pretty) +
  labs(x = NULL, y = "Debt / GDP")
```

## PMI: Manufacturing

```{r}
window(DTM, start=2016) |> 
  subset(select=startsWith(colnames(DTM), "PMIM")) |> 
  scale() |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |> 
  ggplot(aes(x = index)) +
  geom_line(aes(y = value, col = name)) +
  geom_abline(slope = 0, intercept = 0, col = "gray") +
  facet_wrap(~ name, scales = "fixed") +
  scale_x_continuous(breaks = pretty) +
  labs(y = NULL, caption = "Normalized by mean and s.d.") +
  coord_cartesian(ylim = c(-2.5, 2.5))
```

## PMI: Service

```{r}
window(DTM, start=2016) |> 
  subset(select=startsWith(colnames(DTM), "PMIS")) |> 
  scale() |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |> 
  ggplot(aes(x = index)) +
  geom_line(aes(y = value, col = name)) +
  geom_abline(slope = 0, intercept = 0, col = "gray") +
  facet_wrap(~ name, scales = "fixed") +
  scale_x_continuous(breaks = pretty) +
  labs(y = NULL, caption = "Normalized by mean and s.d.")
```

## PMI: Construction

```{r}
window(DTM, start=2016) |> 
  subset(select=startsWith(colnames(DTM), "PMIC")) |> 
  scale() |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |> 
  ggplot(aes(x = index)) +
  geom_line(aes(y = value, col = name)) +
  geom_abline(slope = 0, intercept = 0, col = "gray") +
  facet_wrap(~ name, scales = "fixed") +
  scale_x_continuous(breaks = pretty) +
  labs(y = NULL, caption = "Normalized by mean and s.d.") +
  coord_cartesian(ylim = c(-2.5, 2.5))
```

## Keqiang Index: Electricity Production

```{r}
# yoy series has missing values in January
# imputation assumes it has the same value as February
dualplot(
  y1 = DTM$`Electricity Production: ytd` |> trans(YTD="avg", seas="x11"),
  y2 = DTM$`Electricity Production: yoy: ytd` |> na.locf(fromLast=T), 
  ylab = "Electricity Production (kWH Mn)", 
  rylab = "YoY YTD change (%)")
```

## Keqiang Index: Traffic

```{r}
# there are no missing values in Jan/Feb in these series
# seasonally-adjusted result for Freight Traffic is not smooth
# significant structure break happens in Passenger Traffic in 2014
subset(DTM, select=c(`Freight Traffic`, `Passenger Traffic`, `Air Passengers`)) |> 
  trans(seas = "x11a") |> 
  window(start = 2016) |>
  broom::tidy() |> 
  ggplot(aes(x = index, y = value, col = series)) +
  geom_line() + labs(x=NULL, y=NULL) +
  facet_wrap(~series, scales = "free_y") +
  scale_x_continuous(breaks = pretty) +
  theme(aspect.ratio = 1)
```


## Real Estate: Construction and Sales

```{r, warning=F}
# duplicated values in Jan/Feb
subset(DTM, select=startsWith(colnames(DTM), "Bld")) |> 
  trans(unit=1/1000, YTD = "avg", seas = "x11") |>
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name", NA), sep=": ") |> 
  ggplot(aes(x = index, y = value, col = name)) +
  geom_line() + labs(x = NULL, y = "Floor Spaces (Sqm mn)") +
  facet_wrap(~name, scales = "free_y") +
  scale_x_continuous(breaks = pretty)
```

## Industrial Enterprises

```{r}
# Jan-Feb values are duplicates
dualplot(
  y1 = DTM$`Industrial: Revenue: ytd` |> trans(YTD="avg", seas="x11"),
  y2 = DTM$`Industrial: Profit: ytd` |> trans(YTD="avg", seas="x11"),
  ylab = "Industrial Revenue (RMB Bn)", 
  rylab = "Industrial Profit (RMB Bn)")
```

## Industrial Production

```{r}
# missing values in both Jan and Feb; interpolation applies
subset(DTM, select=startsWith(colnames(DTM), "IP")) |> 
  trans(na_impute = "interp", seas = "x11") |> 
  window(start=2016) |>
  broom::tidy() |> 
  tidyr::separate(series, c(NA, 'name'), sep=": ") |> 
  ggplot(aes(x = index)) +
  geom_line(aes(y = value, col = name)) +
  facet_wrap(~name, scales = "free_y") +
  scale_x_continuous(breaks = pretty) +
  scale_y_continuous(labels = scales::label_number_si()) +
  labs(y = NULL, caption = "Missing values in Jan/Feb interpolated")
```

## Money Supply M1

```{r}
# official seasonally adjusted money aggregates are available
# but they are not up-to-date
dualplot(
  y1 = DTM$M1 |> trans(seas="x11a") |> diff(),
  y2 = DTM$`M1: yoy`, 
  ylab = "MoM Change (RMB Bn)", 
  rylab = "YoY Growth (%)")
abline(h=0, col="gray")
```

## Money Supply M2

```{r}
dualplot(
  y1 = DTM$M2 |> trans(seas="x11a") |> diff(),
  y2 = DTM$`M2: yoy`, 
  ylab = "MoM Change (RMB Bn)", 
  rylab = "YoY Growth (%)")
abline(h=0, col="gray")
```

## Aggregate Financing: New Increased

```{r}
subset(DTM, select=startsWith(colnames(DTM), "AFNI")) |> 
  trans(seas = "x11a") |>
  window(start = 2016) |>
  broom::tidy() |> 
  tidyr::separate(series, c(NA, 'name'), sep=": ") |> 
  ggplot(aes(x = index)) +
  geom_line(aes(y = value, col = name)) +
  facet_wrap(~ name, scales = "free_y") +
  scale_x_continuous(breaks = pretty) +
  scale_y_continuous(labels = scales::label_number()) +
  labs(x= NULL, y = NULL)
```

## Bank Loans: New Increased

```{r}
subset(DTM, select=startsWith(colnames(DTM), "Loan")) |> 
  trans(seas = "x11a") |>
  window(start = 2016) |>
  broom::tidy() |> 
  tidyr::separate(series, c("name", "type", "term"), sep = ": ") |> 
  ggplot(aes(x = index, y = value, col = term)) +
  geom_line() + 
  facet_wrap(~ type, scales = "free_y") +
  scale_x_continuous(breaks = pretty) +
  theme(legend.position = "bottom") + 
  labs(x = NULL, y = NULL)
```


## Interest Rates

```{r}
# LPR starts available in 2019
with(window(DTM, start=2016), {
  dualplot(
    y1 = `LPR: 1Y`, 
    y2 = DR007,
    ylab = "1-Year Loan Prime Rate", 
    rylab = "7-Day Interbank Repo Rate")
})
```

## Treasury Yields

```{r}
subset(DTM, select=startsWith(colnames(DTM), "TB")) |> 
  broom::tidy() |> 
  ggplot(aes(x = index, y = value, col = series)) +
  geom_line() + labs(x=NULL, y="Spot Yield %") + 
  scale_x_continuous(n.breaks = 10) +
  theme(legend.position = "bottom")
```

## Local Government Debt

```{r}
# data starts available in 2017
# seasonal adjustment does not give sensible results due to limited observations
window(DTM, start=2017) |> 
  subset(select=startsWith(colnames(DTM), "Gov Debt")) |> 
  trans(unit=1/1000, chg="ttm") |>
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |>
  ggplot(aes(x = index, y = value, col = name)) +
  geom_line() + labs(x = NULL, y = "Debt Issuance (RMB Bn TTM)") +
  facet_wrap(~name, scales = "free_y") +
  scale_x_continuous(breaks = pretty)
```

## Import and Export

```{r}
subset(DTM, select=c(Import, Export)) |>
  trans(unit=1/1000, seas = "x11a") |>
  multiplot(screens=1, col=2:3, xlab='', main='',
            ylab=c("Import vs Export (USD Bn SA)"))
```

## Trade Balance and Exchange Rate

```{r}
dualplot(
  y1 = DTM$`Trade Balance` |> trans(unit=1/1000, seas="x11a"), 
  y2 = DTM$RMBUSD^(-1), 
  ylab = "Trade Balance (USD Bn)", 
  rylab = "CNY / USD")
```


## Balance of Payments

```{r}
# Net Export: CR+; FDI Inflow: CR+; Forex Receipt: DR-; Reserve Accu.: DR-. 
# Disguised capital outflow: 1. Export without cash receipt (Errors--); 
# 2. Hide export or exaggerate import (shrinked C.A.); 3. Hided oversea 
# investment (F.A.++Errors--). 4. Underground Forex exchange (no record)

subset(DTQ, select=startsWith(colnames(DTQ), "BoP")) |> 
  broom::tidy() |> 
  tidyr::replace_na(list(value=0)) |> 
  ggplot(aes(index, value/1000, fill=series)) +
  geom_col(position = "stack") +
  scale_fill_manual(values=c(2,8,4,7)) +
  scale_x_continuous(breaks = scales::pretty_breaks()) +
  labs(x = NULL, y = "BoP (Quarterly USD Bn)", fill=NULL) +
  theme(legend.position = "bottom")
```

## RMB Assets Hold by Foreign Entities

```{r}
# SSE-HKSE connect is launched in 2014
window(DTM, start=2014) |> 
  subset(select=startsWith(colnames(DTM), "RMB:")) |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |>
  ggplot(aes(x = index, y = value, col = name)) +
  geom_line() + labs(x = NULL, y = "RMB Asset (Billion)") +
  facet_wrap(~name, scales = "free_y") +
  scale_x_continuous(breaks = pretty)
```

## Equity Market

```{r}
# only show most recent movement in equity index
window(DTM, start=2018) |> 
  subset(select=startsWith(colnames(DTM), "CSI")) |> 
  trans(chg = "idx") |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |>
  ggplot(aes(x = index, y = value, col = name)) +
  geom_line() + labs(x = NULL, y = NULL) +
  geom_abline(slope = 0, intercept = 1, col = "gray") +
  facet_wrap(~name, scales = "free_y") +
  scale_x_continuous(n.breaks = 4) +
  labs(caption = "Indexes are normalized to start at 1")
```

## Commodity Market

```{r}
window(DTM, start=2018) |> 
  subset(select=startsWith(colnames(DTM), "SF")) |> 
  trans(chg = "idx") |> 
  broom::tidy() |> 
  tidyr::separate(series, c(NA, "name"), sep=": ") |>
  ggplot(aes(x = index, y = value, col = name)) +
  geom_line() + labs(x = NULL, y = NULL) +
  geom_abline(slope = 0, intercept = 1, col = "gray") +
  facet_wrap(~name, scales = "free_y") +
  scale_x_continuous(n.breaks = 4) +
  labs(caption = "Indexes are normalized to start at 1")
```

<!-- THE END -->
