---
title: "China Economy Chart Pack"
date: "April 2021"
output: 
  beamer_presentation:
    colortheme: dove
---

<!-- TODO List:  -->
<!-- 1. Check accounting unit (billion, million, etc.) -->
<!-- 2. Use facet to replace patchwork whenever possible -->
<!-- 3. Use shortened label to replace original names -->
<!-- 4. Remember to drop NA before plotting -->
<!-- 5. Specify time horizon for each plot -->

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(lubridate)
library(patchwork)
library(scales)
```

```{r, include=FALSE}
ggplot2::theme_set(theme_bw() + theme(
  panel.grid.major.x = element_blank(), 
  panel.grid.minor.x = element_blank(), 
  panel.grid.minor.y = element_blank(),
  strip.background = element_blank(),
  legend.title = element_blank(), 
  legend.position = "bottom", 
  axis.title = element_blank(),
  plot.caption = element_text(hjust=0),
  plot.title = element_text(hjust=.5)
  ))
ggplot2::update_geom_defaults("line", list(color="red"))
```

```{r, eval=FALSE, include=FALSE}
source("ceic.R")
ceic <- ceic_load("data.m")
data <- ceic$fetch_all()
saveRDS(data, "data.Rda")
```

```{r, include=FALSE}
data <- readRDS("data.Rda")
```

```{r, include=FALSE}
meta <- names(data) %>% as_tibble()
meta %>% write_csv("meta.csv")
```

```{r, include=FALSE}
shorten_name <- function(name, level=1, prefix=NULL, suffix=NULL, exclude=NULL) {
  map_chr(name, function(.name) {
    trms <- str_split(.name, ": ", simplify = T)
    excl <- str_c(c("CN", "YoY", "ytd", exclude), collapse = "|")
    subs <- str_subset(trms, excl, negate = T)
    comb <- str_c(tail(subs, level), collapse = ":")
    str_c(prefix, comb, suffix, sep = " ")
  })
}
```

```{r time-horizon}
last_one_year <- 12
last_two_years <- 12*2
last_three_years <- 12*3
last_five_years <- 12*5
last_ten_years <- 12*10
last_forty_years <- 12*20
```

# Overview

## Gross Demestic Product

```{r, fig.asp=0.4}
gdp <- data %>% 
  select(Date, `CN: GDP`, `CN: GDP.1`) %>% 
  filter(!is.na(`CN: GDP`)) 

p1 <- gdp %>% 
  ggplot(aes(x=Date, y=`CN: GDP`)) + 
  geom_line() + 
  labs(y="GDP (SA, ¥Bn)", x=NULL) + 
  scale_x_date(date_breaks = "year", date_labels = "%y") 

p2 <- gdp %>% 
  ggplot(aes(x=Date, y=`CN: GDP.1`)) + 
  geom_line() + 
  labs(y="GDP (SA, Cyclical)", x=NULL) + 
  scale_x_date(date_breaks = "year", date_labels = "%y") 

p1 + p2
```

## Inflation

```{r, warning=F, fig.asp=0.4}
prices <- data %>% 
  select(Date, 
         `CN: Consumer Price Index`, 
         `CN: CPI: Core (excl. Food & Energy)`, 
         `CN: Producer Price Index(PPI)`)  

p1 <- prices %>% 
  select(1:3) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value, color=name)) +
  geom_line() + 
  labs(y = "CPI (last year = 100)", x = NULL) + 
  scale_x_date(date_breaks = "year", date_labels = "%y") + 
  theme(legend.position = "bottom", legend.title = element_blank())

p2 <- prices %>% 
  ggplot(aes(x=Date, y=`CN: Producer Price Index(PPI)`)) + 
  geom_line() + 
  labs(y = "PPI (last year = 100)", x = NULL) + 
  scale_x_date(date_breaks = "year", date_labels = "%y")

p1 + p2
```

## Unemployment

```{r}
data %>% 
  select(Date, 
         `CN: Unemployment Rate: Urban Survey`, 
         `CN: Unemployment Rate: 31-City Survey`) %>% 
  filter(year(Date) > 2016) %>% 
  fill(!Date, .direction = "down") %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value, color=name)) + 
  scale_x_date(date_breaks = "3 months", date_labels = "%b-%y") + 
  labs(y = "Unemployment Rate", x=NULL) + 
  geom_line() 
```

## Leverage Ratio

```{r}
data %>% 
  select(Date,
         `CN: Leverage Ratio: Local Government`, 
         `CN: Leverage Ratio: Non-financial Sector`, 
         `CN: Leverage Ratio: Non-financial Enterprise`,
         `CN: Leverage Ratio: Household`) %>% 
  filter(!is.na(`CN: Leverage Ratio: Household`)) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value, color=name)) + 
  scale_x_date(date_breaks = "year", date_labels = "%y") + 
  scale_y_continuous(n.breaks = 10) + 
  labs(x=NULL, y="% GDP") +
  geom_line()
```

# Economic Activity

## PMI: Manufacturing

```{r}
data %>% 
  select(Date, contains("PMI: Mfg")) %>% 
  tail(n=18) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=name, fill=value)) + 
  geom_tile() + 
  labs(x=NULL, y=NULL) + 
  scale_x_date(date_breaks = "3 months", date_labels = "%b-%y", expand = c(0,0)) +
  scale_fill_gradient2(low = "steelblue4", high = "red4", midpoint = 0) +
  scale_y_discrete(position = "right", expand = c(0,0))
```

## PMI: Non-manufacturing

```{r}
p1<-data %>% 
  select(Date, contains("PMI: Service")) %>% 
  tail(n=18) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=name, fill=value)) + 
  geom_tile() + 
  labs(x=NULL, y=NULL) + 
  scale_x_date(date_breaks = "3 months", date_labels = "%b-%y", expand = c(0,0)) +
  scale_fill_gradient2(low = "steelblue4", high = "red4", midpoint = 0) +
  scale_y_discrete(position = "right", expand = c(0,0)) +
  theme(legend.position = "none")
p2<-data %>% 
  select(Date, contains("PMI: Construction")) %>% 
  tail(n=18) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=name, fill=value)) + 
  geom_tile() + 
  labs(x=NULL, y=NULL) + 
  scale_x_date(date_breaks = "3 months", date_labels = "%b-%y", expand = c(0,0)) +
  scale_fill_gradient2(low = "steelblue4", high = "red4", midpoint = 0) +
  scale_y_discrete(position = "right", expand = c(0,0))

p1/p2
```

## Electricity and Transportation

```{r, warning=F, fig.asp=0.4}
p1<-data %>% 
  select(Date, Power = `CN: Industrial Production: ytd: Power Generated`) %>% 
  filter(year(Date) > 2016) %>% 
  ggplot(aes(x=Date, y=Power)) +
  geom_line() + 
  labs(x=NULL, y="Power generated (TTM, Billion KWh) ") 

p2<-data %>% 
  select(Date, Freight = `CN: Transport: Freight Traffic`) %>% 
  ggplot(aes(x=Date, y=Freight)) + 
  labs(x=NULL, y="Freight traffic (TTM, Million Ton)") + 
  geom_line() +
  scale_x_date(date_breaks = "2 years", date_labels = "%Y")

p1 + p2
```

## Retail Sales

```{r, warning=F, fig.asp=0.4}
p1<-data %>% 
  select(Date, Sales = `CN: Retail Sales of Consumer Goods`) %>% 
  filter(year(Date) > 2016) %>% 
  ggplot(aes(x=Date, y=Sales)) + 
  labs(x=NULL, y="Retail Sales (TTM, Billion RMB)") +
  geom_line()

p2<-data %>% 
  select(Date, Sales = `CN: Online Retail Sales: ytd: Goods and Service`) %>% 
  filter(year(Date) > 2016) %>% 
  ggplot(aes(x=Date, y=Sales)) + 
  labs(x=NULL, y="Online Retail Sales (TTM, Billion RMB)") +
  geom_line()

p1 + p2
```

<!-- ## Online Sales and Volume -->

```{r, warning=F, fig.asp=0.4, include=F}
p1<-data %>% 
  select(Date, Sales = `CN: Taobao and Tmall Online Sales: Value`) %>% 
  filter(year(Date) > 2019) %>% 
  ggplot(aes(x=Date, y=Sales)) + 
  labs(x=NULL, y="Taobao/Tmall Online Sales (TTM, Million RMB)") +
  geom_line()

p2<-data %>% 
  select(Date, Volume = `CN: Taobao and Tmall Online Sales: Volume`) %>% 
  filter(year(Date) > 2019) %>% 
  ggplot(aes(x=Date, y=Volume)) + 
  labs(x=NULL, y="Online Retail Sales (TTM, Million Unit)") +
  geom_line()

p1 + p2
```

## Industrial Production

```{r, warning=F}
data %>% 
  select(Date, contains("Industrial Production")) %>% 
  select(!contains("Power Generated")) %>% 
  filter(year(Date) > 2016) %>% 
  pivot_longer(!Date) %>% 
  mutate(name2 = substring(name, str_length("CN: Industrial Production: "))) %>% 
  ggplot(aes(x=Date,y=value)) +
  geom_line() + 
  labs(x=NULL, y="Units (TTM)") +
  facet_wrap(.~name2, scales = "free_y") + 
  theme_light() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

# Money and Financing

## Money Supply

```{r, warning=F}
data %>% 
  select(Date, contains("Money Supply")) %>% 
  filter(year(Date) > 2016) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value)) +
  geom_line() + 
  labs(x=NULL, y=NULL) +
  facet_wrap(~name, scales = "free_y")
```

## Aggregate Financing

```{r, warning=F}
data %>% 
  select(Date, contains("Aggregate Financing")) %>% 
  tail(12*5) %>% 
  pivot_longer(!Date) %>% 
  mutate(name2 = substring(name, str_length("CN: Aggregate Financing: New Increased: "))) %>% 
  ggplot(aes(x=Date, y=value)) +
  facet_wrap(~name2, scales = "free_y") +
  geom_line() +
  labs(x=NULL, y="New Increased (TTM, Billion RMB)")
```

## Loans: Non-financial Corporation

```{r, warning=F}
data %>% 
  select(Date, contains("Non Financial Enterprise and Govt Agency & Org:")) %>% 
  tail(12*10) %>% 
  pivot_longer(!Date) %>% 
  mutate(name2 = substring(name, str_length("CN: Loan: New Increased: Non Financial Enterprise and Govt Agency & Org: "))) %>% 
  ggplot(aes(x=Date, y=value, color=name2)) +
  geom_line() + 
  labs(x=NULL, y="New Increased (TTM, Billion RMB)") 
```

## Loans: Household

```{r, warning=F}
data %>% 
  select(Date, contains("CN: Loan: New Increased: Household:")) %>% 
  tail(12*10) %>% 
  pivot_longer(!Date) %>% 
  mutate(name2 = substring(name, str_length("CN: Loan: New Increased: Household: "))) %>% 
  ggplot(aes(x=Date, y=value, color=name2)) +
  geom_line() + 
  labs(x=NULL, y="New Increased (TTM, Billion RMB)") 
```

## Loan Prime Rate (LPR)

```{r, warning=F}
data %>% 
  select(Date, contains("Loan Prime Rate")) %>% 
  filter(year(Date) > 2018) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value, color=name)) +
  geom_line() +
  labs(x=NULL, y=NULL)
```

## Interbank Rate

```{r}
data %>% 
  select(Date, contains(c("SHIBOR", "R007"))) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value, color=name)) +
  geom_line() + labs(x=NULL, y=NULL) 
```

## Treasury Yield

```{r}
data %>% 
  select(Date, contains("Treasury Bond Yield")) %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(x=Date, y=value, color=name)) +
  geom_line() + labs(x=NULL, y=NULL) 
```

# Business

## Industrial enterprises

```{r}
data %>% 
  select(Date, contains(c("Industrial Enterprise", "Industrial Capacity"))) %>% 
  tail(last_five_years) %>% 
  fill(!Date, .direction = "down") %>% 
  pivot_longer(!Date) %>% 
  mutate(name2 = shorten_name(name, level=2)) %>% 
  ggplot(aes(Date, value)) + geom_line() +
  facet_wrap(~name2, scales = "free_y") +
  labs(caption = "Revenue and profit are ths sums of trailing 12 months.\nInventory is the seasonally adjusted level divided by 12-month revenue.")
```


<!-- ## Industrial value-added -->

```{r, include=FALSE}
data %>% 
  select(Date, contains("Value Added of Industry")) %>% 
  fill(!Date, .direction = "down") %>% 
  pivot_longer(!Date) %>% 
  ggplot(aes(Date, value, color=name)) + geom_line()
```


## Investments

```{r, warning=F}
data %>% 
  select(Date, contains(c("Fixed Asset Investment", "FAI", "FDI"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label = shorten_name(name, level=2)) %>% 
  ggplot(aes(Date, value)) + geom_line() +
  facet_wrap(~label, scales = "free_y") +
  labs(caption = "Sum of trailing 12 months")
```

# Housing 

## Real estate sales and investmant

```{r, warning=F}
data %>% 
  select(Date, contains(c("Real Estate Inv", "Building Sold"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label = shorten_name(name, level=1)) %>% 
  ggplot(aes(Date, value)) + geom_line() +
  facet_wrap(~label, scales = "free_y") +
  labs(caption = "Sum of trailing 12 months") +
  theme(aspect.ratio = 1) 
```

## Floor space statistics

```{r, warning=F}
data %>% 
  select(Date, contains("Floor Space")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label=shorten_name(name, exclude="Commodity Bldg")) %>% 
  ggplot(aes(Date,value)) + geom_line() +
  facet_wrap(~label, scales = "free_y") + 
  labs(caption = "Sum of trailing 12 months")
```

## Government revenue and expenditure

```{r}
data %>% 
  select(Date, contains(c("Govt Revenue", "Govt Expenditure"))) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(Date, value, color=label)) + geom_line() +
  labs(caption = "Sum of trailing 12 months")
```

## Government debt

```{r}
data %>% 
  select(Date, contains("Local Government Debt Issuance:")) %>% 
  tail(last_three_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label = shorten_name(name, 2)) %>% 
  ggplot(aes(Date, value)) + geom_line() +
  facet_wrap(~label) +
  scale_y_continuous(labels = label_number_si()) +
  labs(caption = "Sum of trailing 12 months")
```

## Trade balance

```{r}
data %>% 
  select(Date, contains(c("Import CIF", "Export FOB", "Trade balance"))) %>% 
  ggplot(aes(x=Date)) + 
  geom_line(aes(y=`CN: Export FOB`, col="Export FOB")) + 
  geom_line(aes(y=`CN: Import CIF`, col="Import CIF")) +
  geom_col(aes(y=`CN: Trade Balance`), fill="grey") +
  scale_y_continuous(labels = label_number_si()) +
  labs(caption = "Seasonally adjusted")
```

## Balance of payments

```{r}
data %>% 
  select(Date, contains("BoP")) %>% 
  tail(last_ten_years) %>% 
  drop_na() %>% 
  pivot_longer(!Date) %>% 
  mutate(label=shorten_name(name, 2, exclude="BoP")) %>% 
  ggplot(aes(Date, value, fill=label)) + 
  geom_col(position = position_stack()) +
  scale_y_continuous(label = label_number_si())
```

## RMB assets hold by oversea entities

```{r}
data %>% 
  select(Date, contains("RMB Financial Asset Held by Overseas Entity")) %>% 
  tail(last_ten_years) %>% 
  drop_na() %>% 
  pivot_longer(!Date) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(Date,value,col=name)) + 
  geom_line() +
  facet_wrap(~label) +
  theme(legend.position = "none")
```

## Equity market

```{r}
data %>% 
  select(Date, contains("CSI 300 Index")) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(Date, value,col=label)) + geom_line() +
  facet_wrap(~label, scales = "free_y") +
  scale_x_date(labels = label_date("%m/%y")) +
  theme(legend.position = "none")
```

## Commodity futures

```{r}
data %>% 
  select(Date, contains(c("Settlement Price", "CCI"))) %>% 
  tail(last_two_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(label=shorten_name(name, exclude="1st Month")) %>% 
  ggplot(aes(Date, value, col=label)) + geom_line() +
  scale_x_date(labels = label_date("%m/%y")) +
  facet_wrap(~label, scales = "free_y") + 
  theme(legend.position = "none")
```

## Bond issuance 

```{r}
P1<-data %>% 
  select(Date, contains("Bond Issuance: PBC:")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(value=value * 10^6) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(Date,value,fill=label)) + 
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  labs(caption = "Sum of trailing 12 months") +
  theme(aspect.ratio = .8, legend.position = "none") +
  ggtitle("Bond issuance")

P2<-data %>% 
  select(Date, contains("Bond Outstanding: PBC:")) %>% 
  tail(last_five_years) %>% 
  pivot_longer(!Date) %>% 
  mutate(value=value * 10^6) %>% 
  mutate(label=shorten_name(name)) %>% 
  ggplot(aes(Date,value,fill=label)) + 
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  ggtitle("Bond outstanding")

P1 + P2
```

## Labor employment

```{r}
P1<-data %>% 
  select(Date, `CN: Employment: Rural`, `CN: Employment: Urban`) %>% 
  drop_na() %>% 
  pivot_longer(!Date) %>% 
  mutate(value = value*10^6) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(Date, value, fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  theme(aspect.ratio = .8)

P2<-data %>% 
  select(Date, 
         `CN: Employment: Primary Industry`, 
         `CN: Employment: Secondary Industry`, 
         `CN: Employment: Tertiary Industry`) %>% 
  drop_na() %>% 
  pivot_longer(!Date) %>% 
  mutate(value = value*10^6) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(Date, value, fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si())

P1 + P2
```

## Employment: urban non-private

```{r}
data %>% 
  select(Date, contains("Employee: Urban Non-private:")) %>% 
  drop_na() %>% 
  pivot_longer(!Date) %>% 
  mutate(value = value * 10^6) %>% 
  mutate(label = shorten_name(name) %>% str_trunc(28)) %>% 
  ggplot(aes(Date,value,fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "right")
```

## Employment: private & individual

```{r}
data %>% 
  select(Date, contains("Employee: Private & Individual:")) %>% 
  filter(!is.na(`CN: No of Employee: Private & Individual: Wholesale & Retail Trade`)) %>% 
  pivot_longer(!Date) %>% 
  mutate(value = value * 10^6) %>% 
  mutate(label = shorten_name(name)) %>% 
  ggplot(aes(Date,value,fill=label)) +
  geom_area(position = position_stack()) +
  scale_y_continuous(labels = label_number_si()) +
  theme(legend.position = "right")
```

<!-- THE END -->